%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Victor}{Gonzalez}
\position{Software Engineer{\enskip\cdotp\enskip}Full Stack Developer}
\address{Las Barrancas 2581, Apt. E203, Quilpué, Chile}

\mobile{(+56) 9 8897 2537}
\email{victor.gonzalezro@gmail.com}
%\homepage{www.posquit0.com}
\github{xzaero}
\linkedin{vagonzal}
\gitlab{xzaero}
\stackoverflow{4848018}{xzaero}
% \twitter{@twit}
\skype{victor.gonzalezro}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Relayr Recruitment Team}
  {Berlin, Germany}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Full Stack Developer}
% How the letter is opened
\letteropening{Dear Sir or Madam,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Victor Gonzalez~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I'm a graduated software engineer with 3 years of formal work experience, and many more years of freelancing and academic work experience. I'm a passionate for new technologies, and extremely passionate for fast, modular and extendable software. I'm very detail oriented, and I would say that I prefer quality over speed almost every time.

I have 2 years of experience as lead developer in the IoT industry for Government entities (Ministry of Energy of Chile, Statal Bank of Chile), and private institutions. In these 2 years of experience, I also worked closesly with energy efficency and sustainability topics, developing software solutions from scratch. My main focus as software engineer is software architecture and project management.

\lettersection{Why Relayr?}
I'm interested in a position for Full Stack Developer because Relayr has one of the most interesting and complete IoT platforms I've ever found. Way back when I found out about the \emph{Wunderbar}, I fell in love with the REST API provided and all the tidbits around the Relayr Dashboard (and the awesome MQTT protocol). So, when I went to visit the Relayr headquarters back in July 2016 due to business inquiries (with Alex Nyahoe and Christian Dittmann), I fell in love with the atmosfere, the diversity, all the exciting and diverse products you were developing, and the overall Relayr company. I wanted to go back ever since.

\lettersection{Why Me?}
I would make a great fit in Relayr because my work experience, my passions and know-how about software development in the IoT industry would help Relayr to achieve the Digital Transformation that Relayr is trying to achieve. I would also help in the near future to lead teams due to my academic profile (which is 5+ years of university studies, with a project management orientation), this way, I could improve the internal processes to make Relayr an even better company. 

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}